{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2018-01-06 thesis/thesis.tex
work on quotes

\input{overview}

@@

\chapter{Related Work}
\inspirationalquote{I see now that none of us are yet ready. The cycle exists so that we may
improve ourselves. But \\
the one who reaches the summit is not our superior, for
they stand on our shoulders to reach it.}
{The Shepherd v82.6.0174, The Talos Principle}

\chapter{Conclusion}
\inspirationalquote{
%	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
%	Why did you make \\ a world that can only grow through cruelty and pain?''
%	\inspirationallinebreak
%
%For a moment--surely this meant death was near--she thought she heard him answer:
%``My child, I \\
%was shaped by the gods that came before me, as you were shaped by me.
%The choice I had was be- \\
%tween creation and oblivion, life and death.
%And I chose life, because any life is better than no life, \\
%because as long as there is life, there is hope--if not for us, then for some generation to come.''
%	\inspirationallinebreak
%
%``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
%	\inspirationallinebreak
%
%``I am a god because I take upon myself the burden of creation,'' the statue replied.
%	\inspirationallinebreak
%
%``Then we are all gods,'' Alexandra said, and pushed the button.}
	\begin{tabular}{p{0.875\textwidth}}
	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?''
	\\
	For a moment--surely this meant death was near--she thought she heard him answer:
	``My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope--if not for us, then for some generation to come.''
	\\
	``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
	\\
	``I am a god because I take upon myself the burden of creation,'' the statue replied.
	\\
	``Then we are all gods,'' Alexandra said, and pushed the button.
	\end{tabular}}
{The Talos Principle (Road to Gehenna)}

>>>>

\input{background}

\chapter{Quicksand}
\inspirationalquote{Somewhere is the promise of an uncharted trail, with 700 branching limbs and 700 ways to fail.}
{ThouShaltNot, ``Cardinal Directions''}

@@

\chapter{Related Work}
\inspirationalquote{
\begin{tabular}{p{0.6\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the ``Related Work'' section.
\end{tabular}}
{Conor McBride, via Twitter}

\chapter{Conclusion}
\inspirationalquote{
%	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
%	Why did you make \\ a world that can only grow through cruelty and pain?''
%	\inspirationallinebreak
%
%For a moment--surely this meant death was near--she thought she heard him answer:
%``My child, I \\
%was shaped by the gods that came before me, as you were shaped by me.
%The choice I had was be- \\
%tween creation and oblivion, life and death.
%And I chose life, because any life is better than no life, \\
%because as long as there is life, there is hope--if not for us, then for some generation to come.''
%	\inspirationallinebreak
%
%``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
%	\inspirationallinebreak
%
%``I am a god because I take upon myself the burden of creation,'' the statue replied.
%	\inspirationallinebreak
%
%``Then we are all gods,'' Alexandra said, and pushed the button.}
	\begin{tabular}{p{0.875\textwidth}}
	``If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?''
	\\
	For a moment--surely this meant death was near--she thought she heard him answer:
	``My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope--if not for us, then for some generation to come.''
	\\
	``Then how are you a god, if you can offer so little?'' she whispered, feeling death creep closer.
	\\
	``I am a god because I take upon myself the burden of creation,'' the statue replied.
	\\
	``Then we are all gods,'' Alexandra said, and pushed the button.
	\end{tabular}}
{The Talos Principle: Road to Gehenna}
